\documentclass[../main.tex]{subfiles}


\begin{abstract} 
The Internet of Things (IoT) is a growing network of devices connected to the Internet. IoT devices range from wearables including smart watches and heart rate monitors, home automation including thermostats, locks, appliances, and Cyber-Physical Systems (CPS) including smart grids and smart healthcare. As IoT/CPS has grown, security, scalability, and resiliency are all critical points of interest for practical,trustworthy systems. At present, many systems contain weak security practices that result in hacks, failures, threats to safety, economic losses, and/or compromised data. 

To address these issues, we propose M-TRA: A Multi-tiered Resilient Architecture for IoT/CPS. M-TRA would allow for a secure, scalable, and resilient system. To provide resiliency, tiers of gateways will form a coalition to determine how edge device traffic flows throughout the system in an effort to distribute the load over the system. For security, trust will be established between devices before a new device enters the system. Once trust is establish, encryption will be used to maintain safe communication between the devices. As the system runs, active monitoring will be deployed to detect anomalies in the system including device failures and hacks using GP-GPU enhanced machine learning. 

The goal of this research is to create a secure, scalable, and resilient IoT/CPS architecture. We will analyze trade-offs in performance as the system scales in size range from 10 devices to 1000s of devices. 


\end{abstract}
