\documentclass[../main.tex]{subfiles}

\begin{document}



\chapter{Publication Plans}

\begin{itemize}
    \item Adding Scalability to Internet of Things Gateways using Parallel Computation of Edge Device Data - 3rd Quarter 2016 - Accepted by: High Performance Extreme Computing Conference - Peer Reviewed IEEE Conference

    
\textbf{Abstract:} The Internet of Things (IoT) is a rapidly growing area with an estimated 25 billion connected devices anticipated   by the year 2020. As more devices join the IoT landscape, the    ability to scale from small to large deployments   is becoming paramount. In this paper, we investigate the ability to scale an IoT system above the leaf-level by using parallel computing within the gateway devices.  The initial task identified  for gateway parallel computing is to aggregate and analyze data from end devices.
This approach provides a scalable architecture for IoT Systems.  Devices such as the Jetson TX1 and TK1 incorporate an ARM multicore plus GP-GPU capability to enhance performance for data-parallel computations.  We demonstrate the value of this type of hybrid architecture on an example IoT system test bed with non-trivial speedup.  This points clearly to the need for gateway devices to move to highly parallel architectures, rather than simply serving as small servers with multiple network adapters.    

    \item Using Machine Learning to Secure IoT Systems - 3rd Quarter 2016 - Submitted to: Privacy, Security and Trust 2016 - Peer Reviewed Conference
    
\textbf{Abstract:} The Internet of Things (IoT) is a massive group of devices containing sensors or actuators connected together over wired or wireless networks. With an estimate of over 25 billion devices connected together by 2020, IoT has been rapidly growing over the past decade. During the growth, security has been identified as one of the weakest areas in IoT. When implementing security within an IoT network, there are several challenges including heterogeneity within the system as well as the quantity of devices that need to be addressed. 


To approach the challenges in securing IoT devices, we propose using machine learning within an IoT gateway to help secure the system. We investigate using Artificial Neural Networks in a gateway to detect anomalies in the data sent from the edge devices. We are convinced that this approach can improve the security of IoT systems.


    \item Using Machine Learning to Monitor System Health in IoT  – 4th Quarter 2016 - Conference TBD
    \item Multi-Tiered Architecture for Internet of Things – 1st Quarter 2017 - Conference TBD
    \item Secure and Lightweight Device-to-Gateway Authentication – 2nd Quarter 2017 - Journal
    \item Using Machine Learning for Anti-Forensics in IoT Systems – 3rd Quarter 2017 - Journal
\end{itemize}

\end{document}