\documentclass[../main.tex]{subfiles}

\begin{document}

\chapter{Research Questions - High Level/Scoping}

The following high level research questions provide the scope of study for this dissertation.

\section{What problem are you trying to solve?}
\begin{itemize}
    \item Make an IoT architecture with tunable QoS, security and resiliency and the ability to scale with economic tradeoffs.
\end{itemize}

\section{What will you know when you're done?}

\begin{itemize}
    \item The systematic tradeoffs of QoS, security, resiliency, and scalability with economic underpinnings.
    \item Identifying the achievable performance of this revised architecture.
    \item Understand and compare old limitations with new limitations (which should be less in several dimensions)
    \item Explain when "one size fits all" and where specific IoT architectures are better
    \item Explain if IoT architectures per service are going to be deployed, and what happens when we try to share an architecture for several "verticals" (e.g., lighting, other).
    \item How scalability, resiliency, and security interact and where key architectural decisions have to be made, consistent with the requirement of economic feasibility for a given design.
\end{itemize}


\section{How will you know when you're done?}

\begin{itemize}
    \item An architecture, with prototype proofs of concept and ability to describe tradeoffs will be achieved.
\end{itemize}


\section{How original is this?}

\begin{itemize}
    \item IoT security, scalability and resiliency are some of the most talked about areas of IoT
    \item Adapting HPC concepts to the system, as well as, multi-tiered gateways, is a new and innovative way of approaching this problem
    \item This architecture will be useful for smart factories, cities, homes, etc.
    \item This architecture could provide a foundation for IoT systems in a wide range of areas including smart grids, hospitals, buildings, etc.

\end{itemize}

\section{Who will care? What's the impact?}

\begin{itemize}
    \item IoT security, scalability and resiliency are some of the most talked about areas of IoT
    \item Adapting HPC concepts to the system, as well as, multi-tiered gateways, is a new and innovative way of approaching this problem
    \item This architecture will be useful for smart factories, cities, homes, etc.
    \item This architecture could provide a foundation for IoT systems in a wide range of areas including smart grids, hospitals, buildings, etc.
\end{itemize}


\section{Why did you select this problem among many?}

\begin{itemize}
    \item A strong, secure foundation is necessary for a strong infrastructure. The IoT infrastructure is new and is in need of strong security measures in an effort to create a stable and resilient infrastructure that can be implemented in factories, cities, homes, etc.
\end{itemize}

\section{Why will this be a significant contribution to the literature in your area?}

\begin{itemize}
    \item Provide an architecture for security and resiliency within an IoT system which currently has limited documentation.
    \item Produce literature on machine learning in IoT systems to provide real-time system monitoring
    \item Produce literature on best practice for secure device to device authentication
\end{itemize}

\end{document}